Submission outcomes by author and gatekeeper characteristics

### 2019-07-30 figures/gatekeeper_author_outcomes/gatekeeper_author_outcomes.Rmd
missed one file

# setup theme
theme_dakota <- function () { 
    theme_bw(base_size=10, base_family="Times") %+replace% 
        theme(
            strip.background = element_blank(),
            #strip.text = element_text(face = "bold"),
            plot.title = element_text(size = 20, face = "bold"),
            axis.text.x = element_text(size = 9, margin = margin(t = 5, b = 5), face = "bold"),
            legend.title = element_blank(),
            strip.text = element_text(size = 11),
            legend.position = "bottom"
        )
}

@@

@@

countries_separate <- elife %>%
  filter(full_decision_made & has_full_submission & ca_country %in% countries) %>%
  group_by(ca_country, la_country_homophily) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_accept_rate = accept_count / paper_count,
    se = 1.96 * sqrt( (encourage_accept_rate * (1 - encourage_accept_rate)) / paper_count),
    encourage_accept_rate = encourage_accept_rate * 100,
    se = se * 100,
    lower = encourage_accept_rate - se,
    upper = encourage_accept_rate + se,
    upper = ifelse(upper > 100, 100, upper)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  left_join(sig_df) %>%
  #top_n(16, totals) %>% # 8 countries, 3 authorship types per country, therefore first 24 rows
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>%
  # Start ggplot
  ggplot(aes(x = la_country_homophily, y = encourage_accept_rate, fill = la_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 7.5), size = 4) +
  geom_text(aes(label = sig, x = 1.5, y = 86), size = 4) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 80, 101), yend = ifelse(sig != "N/A", 80, 101)), color = "black") +
  facet_wrap(~ca_country, nrow = 2, ncol = 4, labeller = label_wrap_gen()) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_y_continuous(limits = c(0, 100), position = "right") +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted",
    title = "D"
  ) +
  theme(
    axis.text.x = element_text(size = 11, angle = 330, vjust = 1, hjust = 0, face = "bold"),
    axis.title.y = element_text(size = 12)
  )

@@

countries_pooled <- d1.summ %>%
  union(d2.summ) %>%
  union(d25.summ) %>%
  #union(d3.summ) %>%
  left_join(sig_df, by = "type") %>%
  mutate(type = factor(type, 
                       levels = c("all", "no us", "no usuk"),
                       labels = c("All Countries", "No U.S.", "No U.S., U.K.")
                       )
         ) %>%
  ggplot(aes(x = la_country_homophily, y = encourage_accept_rate, fill = la_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 10), size = 4) +
  geom_text(aes(label = sig, x = 1.5, y = 85), size = 4) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 80, 101), yend = ifelse(sig != "N/A", 80, 101)), color = "black") +
  facet_wrap(~type, ncol = 4, labeller = label_wrap_gen(20)) +
  coord_cartesian(ylim = c(0.0, 100)) +
  theme_dakota() +
  guides(fill = FALSE) +
  ylim(0, 1) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  scale_y_continuous(position = "right") +
  labs(
    x = "",
    y = "% of full submissions accepted",
    title = "C"
  ) +
  theme(axis.text.x = element_text(size = 11, angle = 330, vjust = 1, hjust = 0, face = "bold"),
        axis.title.y = element_text(size = 12))

@@

### Presence of author-reviewer national homogeny by country of correposnding author
```{r rows.print = 20}
full <- elife %>% 
  filter(has_full_submission) %>%
  group_by(ca_country) %>%
  summarize(
    submissions = n(),
    prop_homogeny = sum(la_country_homophily, na.rm = T) / submissions
  ) %>%
  arrange(-prop_homogeny) %>%
  top_n(20) %>%
  mutate(prop_homogeny = round(prop_homogeny, 3))

names(full) <- c("Country", "# Submissions", "% Country Homogeneity")

stargazer(full, type = "latex", summary = FALSE, rownames = FALSE, font.size = "scriptsize", digits = )
```

@@

```{r}
g1 <- grid.arrange(countries_pooled, countries_separate, ncol = 1, heights = 2:3)
g <- grid.arrange(gender_homophily, g1, ncol = 2)
```

```{r}
## Save the file
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = g, height = 8, width = 10)
```

>>>>

# setup theme
theme_dakota <- function () { 
    theme_bw(base_size=10, base_family="Times") %+replace% 
        theme(
            strip.background = element_blank(),
            #strip.text = element_text(face = "bold"),
            plot.title = element_text(size = 20, face = "bold"),
            axis.text.x = element_text(size = 12, margin = margin(t = 5, b = 5), face = "bold"),
            legend.title = element_blank(),
            strip.text = element_text(size = 11),
            legend.position = "bottom"
        )
}

@@

```{r}
library(ggrepel)
head(data_homophily)
gender_homophily <- data_homophily %>%
  mutate(composition = factor(composition, levels = c("All-female", "Mixed-gender", "All-male"))) %>%
  ggplot(aes(x = composition, y = acceptance_rate, color = gender, shape = gender, group = gender)) +
  geom_line(alpha = 0.5, width = 0.5) +
  geom_point(size = 3) +
  facet_wrap(~author_key, ncol = 1) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.1, alpha = 0.8) + 
  coord_cartesian(ylim = c(30, 80)) +
  geom_text_repel(aes(label = paste0(round(acceptance_rate, 1), "%")), hjust = 1.5, vjust = -3, size = 3, 
                  segment.alpha = 0.6, segmnet.size = 0.1, force = 50, segment.color = "grey") +
  theme_dakota() +
  scale_color_discrete(name = "Author Gender") +
  scale_shape_discrete(name = "Author Gender") +
  labs(y = "% of full submissions accepted",
       x = "Reviewer Team Composition",
       title = "A") +
  theme(
    #axis.title.x = element_text(face = "bold", size = 11),
        axis.title.x = element_blank(),
        axis.text.x = element_text(face = "bold", angle = 30, hjust = 1, vjust = 1, size = 11),
        axis.text.y = element_text(size = 10),
        axis.title.y = element_text(size = 12),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 11),
        legend.position = "bottom",
        strip.text.x = element_text(size = 12),
        strip.text.y = element_text(size = 14, face = "bold"))

gender_homophily
ggsave("~/Desktop/elife_lineplot.png", gender_homophily, height = 7, width = 7)
```

@@

countries_separate <- elife %>%
  filter(full_decision_made & has_full_submission & ca_country %in% countries) %>%
  group_by(ca_country, la_country_homophily) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_accept_rate = accept_count / paper_count,
    se = 1.96 * sqrt( (encourage_accept_rate * (1 - encourage_accept_rate)) / paper_count),
    encourage_accept_rate = encourage_accept_rate * 100,
    se = se * 100,
    lower = encourage_accept_rate - se,
    upper = encourage_accept_rate + se,
    upper = ifelse(upper > 100, 100, upper)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  left_join(sig_df) %>%
  mutate(ca_country = ifelse(ca_country == "United States", "U.S.", ifelse(ca_country == "United Kingdom", "U.K.", ca_country))) %>%
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>%
  # Start ggplot
  ggplot(aes(x = la_country_homophily, y = encourage_accept_rate, fill = la_country_homophily)) +
    geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
    geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
    #geom_text(aes(label = paper_count, y = 7.5), size = 4) +
    geom_text(aes(label = paste0(round(encourage_accept_rate, 1), "%"), y = upper + 8), size = 3) +
    geom_text(aes(label = sig, x = 1.5, y = 96), size = 4) +
    geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 90, 101), yend = ifelse(sig != "N/A", 90, 101)), color = "black") +
    facet_wrap(~ca_country, nrow = 2, ncol = 4, labeller = label_wrap_gen()) +
    theme_dakota() +
    guides(fill = FALSE) +
    scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
    scale_y_continuous(limits = c(0, 100), position = "right") +
    scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
    labs(
      x = "",
      y = "% of full submissions accepted",
      title = "C"
    ) +
    theme(
      strip.text = element_text(size = 13),
      axis.text.x = element_text(size = 11, angle = 330, vjust = 1, hjust = 0, face = "bold"),
      axis.title.y = element_text(size = 12),
      plot.title = element_text(size = 22, face = "bold")
    )

@@

countries_pooled <- d1.summ %>%
  union(d2.summ) %>%
  union(d25.summ) %>%
  #union(d3.summ) %>%
  left_join(sig_df, by = "type") %>%
  mutate(type = factor(type, 
                       levels = c("all", "no us", "no usuk"),
                       labels = c("All Countries", "No U.S.", "No U.S., U.K.")
                       )
         ) %>%
  ggplot(aes(x = la_country_homophily, y = encourage_accept_rate, fill = la_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  #geom_text(aes(label = paper_count, y = 10), size = 4) +
  geom_text(aes(label = paste0(round(encourage_accept_rate, 1), "%"), y = upper + 8), size = 3) +
  geom_text(aes(label = sig, x = 1.5, y = 96), size = 4) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 90, 101), yend = ifelse(sig != "N/A", 90, 101)), color = "black") +
  facet_wrap(~type, ncol = 4, labeller = label_wrap_gen(20)) +
  coord_cartesian(ylim = c(0.0, 100)) +
  theme_dakota() +
  guides(fill = FALSE) +
  ylim(0, 1) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  scale_y_continuous(position = "right") +
  labs(
    x = "",
    y = "% of full submissions accepted",
    title = "B"
  ) +
  theme(axis.text.x = element_text(size = 11, angle = 330, vjust = 1, hjust = 0, face = "bold"),
        axis.title.y = element_text(size = 12),
        strip.text = element_text(size = 12))

@@

### Presence of author-reviewer national homogeny by country of correposnding author
```{r rows.print = 20}
full <- elife %>% 
  filter(has_full_submission & !is.na(la_country)) %>%
  group_by(ca_country) %>%
  summarize(
    submissions = n(),
    num_homogeny =  sum(la_country_homophily, na.rm = T),
    prop_homogeny = num_homogeny / submissions
  ) %>%
  arrange(-prop_homogeny) %>%
  top_n(20) %>%
  mutate(prop_homogeny = round(prop_homogeny, 3))

names(full) <- c("Country", "# Submissions", "# Homogeneity", "% Country Homogeneity")

stargazer(full, type = "latex", summary = FALSE, rownames = FALSE, font.size = "scriptsize")
```

@@

```{r}
g1 <- grid.arrange(countries_pooled, countries_separate, ncol = 1, heights = 2:3)
g <- grid.arrange(gender_homophily, g1, ncol = , widths = 2:3)
```

```{r}
## Save the file
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = g, height = 7, width = 8)
```
